Index measures for oak decline severity using phenotypic descriptors

### 2019-12-12 manuscript/manuscript.Rmd
added t-test results

```{r loadData, include = FALSE}
loadd(site_rf_margin)
loadd(site_rf_post_correction_margin)
```

@@

A total of 30 phenotypic descriptors were collected relating to the trees shape, size, crown condition and the presence of biotic agents including insects, bacteria and fungi.
These descriptors are shown in Table #.
Crown radius, canopy closure and tap tests for dead stem tissue were measured for each cardinal point.
AOD stem symptoms (active bleeds, black staining, callused wounds) were collected from the basel 3m of the stem.
Each individual 
All trees were manually assigned a decline status category; healthy, AOD, COD or remission.

@@

R v`r str_c(version$major,version$minor,sep ='.')` was used for all parsing, preparation and analysis of phenotypic data [@R2019].

@@

The code used to generate the decline indexes is available as an R package pdi (v) at https://github.com/jasenfinch/pdi.
All raw data and code used to generate this manuscript are available at https://github.com/jasenfinch/Index_measures_for_oak_decline_severity_using_phenotypic_descriptors.

@@

@@

Proximity matrix ($$P$$) was transformed to a dissimilarity ($$1 - P$$) then multidimensional scaling (MDS) to 2 dimensions applied.
The first dimension was found to be related to the overall severity of decline.
It was min-max scaled to give the PDI a scale between 0 and 1 with more severely declining trees having a score closer to 1.
The second MDS dimension was found to be associated with  min-max scaled to give scores between -1 and 1 with chronically declining trees having a score closer to -1 and acutely declining trees having a score closer to 1. 
Trees with a score around 0 are neither distinctively AOD or COD sharing characteristics of both conditions in trees with PDI greater than 0.3.
The PDI and DAI indexes are plotted for all 174 trees in Figure # showing the relationship with the

>>>>

```{r loadData, include = FALSE}
loadd(site_rf_margin,
      site_rf_post_correction_margin,
      PDI_status_ttest,
      DAI_groups_ttest)
```

@@

A total of 30 phenotypic descriptors were collected relating to the trees shape, size, crown condition and the presence of biotic agents including insects, bacteria and fungi.
These descriptors are shown in Table #.
Crown radius, canopy closure and tap tests for dead stem tissue were measured for each cardinal point.
AOD stem symptoms (active bleeds, black staining, callused wounds) were collected from the basel 3m of the stem.
Each individual 
All trees were manually assigned a decline status category; control, AOD, COD or remission.

@@

R v`r str_c(version$major,version$minor,sep ='.')` was used for all parsing, preparation and analysis of phenotypic data [@R2019].
The code used to generate the decline indexes is available as an R package pdi (v) at https://github.com/jasenfinch/pdi.
All raw data and code used to generate this manuscript are available at https://github.com/jasenfinch/Index_measures_for_oak_decline_severity_using_phenotypic_descriptors.

@@

@@

The randomForest R package

@@

Proximity matrix (*P*) was transformed to a dissimilarity (1 - *P*) then multidimensional scaling (MDS) to 2 dimensions applied.
The first dimension was found to be related to the overall severity of decline.
It was min-max scaled to give the PDI a scale between 0 and 1 with more severely declining trees having a score closer to 1.
The second MDS dimension was found to be associated with  min-max scaled to give scores between -1 and 1 with chronically declining trees having a score closer to -1 and acutely declining trees having a score closer to 1. 
Trees with a score around 0 are neither distinctively AOD or COD sharing characteristics of both conditions in trees with PDI greater than 0.3.
A significant difference was found in the PDI between non-symptomatic (control) and symptomatic (AOD and COD) decline statuses using an independant two sample t-test (`r glue("t({PDI_status_ttest$parameter}) = {signif(PDI_status_ttest$statistic,digits = 3) %>% abs()}, p < 0.001")`) with group means of `r signif(PDI_status_ttest$estimate1,digits = 3)` and `r signif(PDI_status_ttest$estimate2,digits = 3)` for non-symptomatic and symptomatic statuses respectively.
Significance was also found in the DAI between the AOD and COD groups (`r glue("t({DAI_groups_ttest$parameter}) = {signif(DAI_groups_ttest$statistic,digits = 3) %>% abs()}, p < 0.001")`) with group means of `r signif(DAI_groups_ttest$estimate1,digits = 3)` and `r signif(DAI_groups_ttest$estimate2,digits = 3)` for the AOD and COD groups respectively.
A scatter plot of PDI against DAI is shown in Figure # for all 174 trees.
It can clearly be seen that the
